Welcome to the open source shared code for C\-A\-S\-C\-A\-D\-E Agent Based Modelling (A\-B\-M) framework. It requires the Repast Simphony A\-B\-M libraries to run. These are available, along with instructions on how to install for your O\-S, from

\begin{quotation}
\href{http://repast.sourceforge.net/}{\tt Repast homepage}

\end{quotation}


The repast download includes a compatible version of Eclipse I\-D\-E. It is possible to use Repast outside the eclipse I\-D\-E, however we have found that the easiest way is to use it within the Eclipse I\-D\-E and will describe the installation and use procedure based on that.

To use the C\-A\-S\-C\-A\-D\-E framework, clone \href{http://www.github.com/rsnape/cascade}{\tt this repository} and then import the project into your Eclipse workspace. Use the \char`\"{}\-Run C\-A\-S\-C\-A\-D\-E model\char`\"{} launch configuration and the C\-A\-S\-C\-A\-D\-E framework should initialise with the default simulation model as defined in the config file Cascade\-Config.\-xml. Press run on the Repast G\-U\-I and you will see the ticks of the simulation advancing.

{\bfseries Please note -\/ this is research project code, subject to revision without notice and A\-P\-I changes etc.}

The research project which developed this code is documented at the \href{http://www.iesd.dmu.ac.uk/~cascade}{\tt C\-A\-S\-C\-A\-D\-E website}.

A further research project (Agent-\/based Modelling of Electricity Networks) has been funded by the \href{http://www.epsrc.ac.uk}{\tt E\-P\-S\-R\-C} to make use of the framework in studying future configurations of the U\-K electricity network. See the award notice \href{http://gow.epsrc.ac.uk/NGBOViewGrant.aspx?GrantRef=EP/K033492/1}{\tt here}

More documentation will follow as C\-A\-S\-C\-A\-D\-E is further developed for widespread use. If you are viewing this page from the A\-P\-I documentation page, please use the links on the left to navigate through our packages and class structure.

If you have questions, comments, suggestions or wish to contribute -\/ please email me jsnape $<$at$>$ dmu\-\_\-ac\-\_\-uk 